The Cost of Transportation : Spatial Analysis of US Fuel Prices

### 2018-02-11 Docs/Communication/ewgt2017.tex
slides_v1

%\textit{Average prices in time by county for regular fuel}

@@

\includegraphics[width=0.5\textwidth,height=0.6\textheight]{figures/moran_days}
\includegraphics[width=0.5\textwidth,height=0.6\textheight]{figures/moran_decay_weeks}

@@

\begin{itemize}
\item Geographically Weighted Regression (GWR)~\cite{brunsdon1996geographically} to tackle spatial non-stationarity : capturing a variable influence in space of explicative variables for prices
\item Multi-modeling using corrected AIC for model selection : find the best model and the best bandwidth controlling for overfitting
\end{itemize}

@@

@@

% method of multi-level

%\begin{eqnarray}
%x_{i,s,c,t} &=& \beta_s + \varepsilon_{i,s,c,t} \\
%x_{i,s,c,t} &=& \beta_c + \varepsilon_{i,s,c,t} \\
%x_{i,s,c,t} &=& \beta_i + \varepsilon_{i,s,c,t}\\
%\end{eqnarray}

@@

@@

\includegraphics[width=0.8\textwidth]{figures/gwr_allbest_residual}

>>>>

@@

\includegraphics[width=0.5\textwidth,height=0.5\textheight]{figures/moran_days}
\includegraphics[width=0.5\textwidth,height=0.5\textheight]{figures/moran_decay_weeks}

@@

\begin{itemize}
\item Geographically Weighted Regression (GWR)~\cite{brunsdon1996geographically} to tackle spatial non-stationarity : capturing a variable influence in space of explicative variables for prices
\medskip
\item Multi-modeling using corrected AIC for model selection : find the best model and the best bandwidth controlling for overfitting
\end{itemize}

@@

\textit{Fitted coefficients and $R^2$ for the best model}

@@

@@

$\rightarrow$ Fundamental role of spatio-temporal non-stationarity and existence of typical stationarity scales

@@

\includegraphics[width=\textwidth]{figures/gwr_allbest_residual}

%%%%%%
\sframe{High dimensional fixed effects}{

With $x_{i,s,c,t}$ the fuel price in day $t$, in gas station $i$, in state $s$ and in county $c$, we start by running high dimensional fixed effect regressions

\begin{eqnarray}
x_{i,s,c,t} &=& \beta_s + \varepsilon_{i,s,c,t} \\
x_{i,s,c,t} &=& \beta_c + \varepsilon_{i,s,c,t} \\
x_{i,s,c,t} &=& \beta_i + \varepsilon_{i,s,c,t}\\
\end{eqnarray}

Where $\varepsilon_{i,s,c,t}$ contains an idiosyncratic error and a day fixed effect.

$\rightarrow$ It confirms that most of the variance can be explained by a state fixed effect and that integrating more accurate levels has only small effect on the fit of our model as measured by the R-squared.
